Lasso_RCI_Response

### 2024-02-27 Lasso_RCI_Response.Rmd
Updated CUXOS / CUDOS > 20

DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "Anxeity: JT indices by disorder")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "Anxeity: JT indices by disorder")

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
tab1_df_anx <- data.frame(table1_tab_anx)

### next gather info based upon depression

@@

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_anx,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
table1_gen 
```

### Treatment information
Overal look at treatment varaibles by treatment response
```{r}
# PHP Treatment information
resp_tab <- data.frame(table1::table1(
   ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab
```

pre-post scores by treatment response - TOGETHER
```{r}
# Treatment scores
#1. Make DF + name columns
Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")

#2. Row 1 - responders
Scores_tab[1,] = c(NA,"Non-responder","Non-responder","Non-responder","Responder","Responder","Responder")

#3. Get statistics for variables + Assign to table
  # Anxiety - CUXOS
    #make df
      anx_rep_tab <- Mothership_post |>
        group_by(RESPONDER_FIGS) |>
        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
                  )
# add to scores tab
        Scores_tab[2,] = c(
          "CUXOS",
          #Non-responder scores
          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
          #responder scores
          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")")
        )

  # Depression - CUDOS
  #Make df
    dep_rep_tab <- Mothership_post |>
      group_by(RESPONDER_FIGS) |>
      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
                )
    #Add to Scores_tab
       Scores_tab[3,] = c(
        "CUDOS",
        #Non-responder scores
        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
        #responder scores
        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")")
      )

  #RDQ subscales
       Scores_tab[4,1] = "RDQ Subscales"

  # Coping
      cope_rep_tab <- Mothership_post |>
        group_by(RESPONDER_FIGS) |>
        summarize(pre_cope = round( mean(rdqPRE_coping, na.rm = TRUE),2),
                  pre_cope_sd = round( sd(rdqPRE_coping, na.rm = TRUE),2),
                  post_cope = round( mean(rdqPOST_coping, na.rm = TRUE),2),
                  post_cope_sd = round( sd(rdqPOST_coping, na.rm = TRUE),2),
                  delta_cope = round( mean(rdq_coping_change, na.rm = TRUE),2),
                  delta_cope_sd = round( sd(rdq_coping_change, na.rm = TRUE),2)
              )
      Scores_tab[5,] = c(
        "Coping",
        #Non-responder scores
        paste0(cope_rep_tab$pre_cope[[1]]," (",cope_rep_tab$pre_cope_sd[[1]],")"),
        paste0(cope_rep_tab$post_cope[[1]]," (",cope_rep_tab$post_cope_sd[[1]],")"),
        paste0(cope_rep_tab$delta_cope[[1]]," (",cope_rep_tab$delta_cope_sd[[1]],")"),
        #responder scores
        paste0(cope_rep_tab$pre_cope[[2]]," (",cope_rep_tab$pre_cope_sd[[2]],")"),
        paste0(cope_rep_tab$post_cope[[2]]," (",cope_rep_tab$post_cope_sd[[2]],")"),
        paste0(cope_rep_tab$delta_cope[[2]]," (",cope_rep_tab$delta_cope_sd[[2]],")")
      )
   # Positive mental health
  pmh_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_pmh = round( mean(rdqPRE_pmh, na.rm = TRUE),2),
              pre_pmh_sd = round( sd(rdqPRE_pmh, na.rm = TRUE),2),
              post_pmh = round( mean(rdqPOST_pmh, na.rm = TRUE),2),
              post_pmh_sd = round( sd(rdqPOST_pmh, na.rm = TRUE),2),
              delta_pmh = round( mean(rdq_pmh_change, na.rm = TRUE),2),
              delta_pmh_sd = round( sd(rdq_pmh_change, na.rm = TRUE),2)
              )
         Scores_tab[6,] = c(
              "Positive Mental Health",
              #Non-responder scores
              paste0(pmh_rep_tab$pre_pmh[[1]]," (",pmh_rep_tab$pre_pmh_sd[[1]],")"),
              paste0(pmh_rep_tab$post_pmh[[1]]," (",pmh_rep_tab$post_pmh_sd[[1]],")"),
              paste0(pmh_rep_tab$delta_pmh[[1]]," (",pmh_rep_tab$delta_pmh_sd[[1]],")"),
              #responder scores
              paste0(pmh_rep_tab$pre_pmh[[2]]," (",pmh_rep_tab$pre_pmh_sd[[2]],")"),
              paste0(pmh_rep_tab$post_pmh[[2]]," (",pmh_rep_tab$post_pmh_sd[[2]],")"),
              paste0(pmh_rep_tab$delta_pmh[[2]]," (",pmh_rep_tab$delta_pmh_sd[[2]],")")
            )
   # Functioning
  func_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_func = round( mean(rdqPRE_func, na.rm = TRUE),2),
              pre_func_sd = round( sd(rdqPRE_func, na.rm = TRUE),2),
              post_func = round( mean(rdqPOST_func, na.rm = TRUE),2),
              post_func_sd = round( sd(rdqPOST_func, na.rm = TRUE),2),
              delta_func = round( mean(rdq_func_change, na.rm = TRUE),2),
              delta_func_sd = round( sd(rdq_func_change, na.rm = TRUE),2)
              )    
         Scores_tab[7,] = c(
              "Functioning",
              #Non-responder scores
              paste0(func_rep_tab$pre_func[[1]]," (",func_rep_tab$pre_func_sd[[1]],")"),
              paste0(func_rep_tab$post_func[[1]]," (",func_rep_tab$post_func_sd[[1]],")"),
              paste0(func_rep_tab$delta_func[[1]]," (",func_rep_tab$delta_func_sd[[1]],")"),
              #responder scores
              paste0(func_rep_tab$pre_func[[2]]," (",func_rep_tab$pre_func_sd[[2]],")"),
              paste0(func_rep_tab$post_func[[2]]," (",func_rep_tab$post_func_sd[[2]],")"),
              paste0(func_rep_tab$delta_func[[2]]," (",func_rep_tab$delta_func_sd[[2]],")")
            )

    # General sense of wellbeing
    wbs_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_wbs = round( mean(rdqPRE_wbs, na.rm = TRUE),2),
              pre_wbs_sd = round( sd(rdqPRE_wbs, na.rm = TRUE),2),
              post_wbs = round( mean(rdqPOST_wbs, na.rm = TRUE),2),
              post_wbs_sd = round( sd(rdqPOST_wbs, na.rm = TRUE),2),
              delta_wbs = round( mean(rdq_wbs_change, na.rm = TRUE),2),
              delta_wbs_sd = round( sd(rdq_wbs_change, na.rm = TRUE),2)
              )

     Scores_tab[8,] = c(
              "General sense of wellbeing",
              #Non-responder scores
              paste0(wbs_rep_tab$pre_wbs[[1]]," (",wbs_rep_tab$pre_wbs_sd[[1]],")"),
              paste0(wbs_rep_tab$post_wbs[[1]]," (",wbs_rep_tab$post_wbs_sd[[1]],")"),
              paste0(wbs_rep_tab$delta_wbs[[1]]," (",wbs_rep_tab$delta_wbs_sd[[1]],")"),
              #responder scores
              paste0(wbs_rep_tab$pre_wbs[[2]]," (",wbs_rep_tab$pre_wbs_sd[[2]],")"),
              paste0(wbs_rep_tab$post_wbs[[2]]," (",wbs_rep_tab$post_wbs_sd[[2]],")"),
              paste0(wbs_rep_tab$delta_wbs[[2]]," (",wbs_rep_tab$delta_wbs_sd[[2]],")")
            )

    #Symptoms
    sym_rep_tab <- Mothership_post |>
    group_by(RESPONDER_FIGS) |>
    summarize(pre_sym = round( mean(rdqPRE_sym, na.rm = TRUE),2),
              pre_sym_sd = round( sd(rdqPRE_sym, na.rm = TRUE),2),
              post_sym = round( mean(rdqPOST_sym, na.rm = TRUE),2),
              post_sym_sd = round( sd(rdqPOST_sym, na.rm = TRUE),2),
              delta_sym = round( mean(rdq_sym_change, na.rm = TRUE),2),
              delta_sym_sd = round( sd(rdq_sym_change, na.rm = TRUE),2)
              )

      Scores_tab[9,] = c(
              "Symptoms",
              #Non-responder scores
              paste0(sym_rep_tab$pre_sym[[1]]," (",sym_rep_tab$pre_sym_sd[[1]],")"),
              paste0(sym_rep_tab$post_sym[[1]]," (",sym_rep_tab$post_sym_sd[[1]],")"),
              paste0(sym_rep_tab$delta_sym[[1]]," (",sym_rep_tab$delta_sym_sd[[1]],")"),
              #responder scores
              paste0(sym_rep_tab$pre_sym[[2]]," (",sym_rep_tab$pre_sym_sd[[2]],")"),
              paste0(sym_rep_tab$post_sym[[2]]," (",sym_rep_tab$post_sym_sd[[2]],")"),
              paste0(sym_rep_tab$delta_sym[[2]]," (",sym_rep_tab$delta_sym_sd[[2]],")")
            )
Scores_tab
```

@@

RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
#anxiety 
RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
# Depresssion
RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
#Total
RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])

>>>>

DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  )

Vars_anx <- Mothership_lasso |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

# Mothership_lasso_dep <- Mothership_post |>
#     filter(
#     !is.na(Some_College),
#     !is.na(Female),
#     !is.na(IPT_track_1),
#     !is.na(White),
#     !is.na(Depression_Responder),
#     CUXOS_pre >= 20,
#     CUDOS_pre >= 20
#   )

Vars_dep <- Mothership_lasso |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

Vars_anx <- na.omit(Vars_anx)
Vars_dep <- na.omit(Vars_dep)

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
tab1_df_anx <- data.frame(table1_tab_anx)
tab1_df_anx
### next gather info based upon depression

@@

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
table1_gen

summary(Mothership_lasso$Depression_Responder)

### Treatment information
Overal look at treatment varaibles by treatment response
```{r}
# PHP Treatment information
# resp_tab <- data.frame(table1::table1(
#    ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
#   data = Mothership_post))
# colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
# resp_tab
```

# RCI analysis Table
pre-post scores by treatment response, cut off, and RCI threshold
```{r}
# Treatment scores
#1. Make DF + name columns
Scores_tab <- data.frame(matrix(nrow = 2 ,ncol=9))
colnames(Scores_tab) = c("Instrument", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)", "Cut Off", "RCI")

#2. Row 1 - responders
Scores_tab[1,] = c(NA,"M (sd)","M (sd)","M (sd)","M (sd)","M (sd)","M (sd)",NA,NA)

#3. Get statistics for variables + Assign to table
  # Anxiety - CUXOS
    #make df
      anx_rep_tab <- Mothership_post |>
        group_by(Anxiety_Responder) |>
        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
                  )
# add to scores tab
        Scores_tab[2,] = c(
          "CUXOS",
          #Non-responder scores
          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")"),
          #responder scores
          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
          20,
          20
        )

# Depression - CUDOS
  #Make df
    dep_rep_tab <- Mothership_post |>
      group_by(Depression_Responder) |>
      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
                )
    #Add to Scores_tab
       Scores_tab[3,] = c(
        "CUDOS",
        #Non-responder scores
        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")"),
        #responder scores
        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
        20,
        13
      )

Scores_tab
```

Figure 1: Pre-post Line Plot
```{r}
#### Redo and recreate dataset for Anxiety or depression response.
AnxDep_response_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(RESPONDER_FIGS)) |>
  group_by(Test,RESPONDER_FIGS,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

@@

RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
#anxiety

RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
# Depresssion
RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
# #Total
# RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
